---
title: "Assignment 5"
author: "Sophia Telles & Samantha Driscoll"
date: "October 3, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(readxl)
tallb=read_excel("tallestbuildings.xlsx")
```
Need to make sure that files are in same session
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r}
head(tallb)
```

# 1 Display how many buildings there are in each city. Arrange the data in descending order of number of buildings.
```{r}
citycounts=tallb%>%group_by(City)%>%summarize(number=length(City))
citycounts
```


```{r}
ggplot(citycounts,aes(reorder(City,number),number))+geom_bar(stat="identity")+coord_flip()+xlab("City")
```


# 2. Plot different cities in order of the mean height of buildings

```{r}
meanb=tallb%>%group_by(City)%>%summarize(number=mean(`Height (ft)`))
meanb
```

```{r}
ggplot(meanb,aes(reorder(City,number),number))+geom_bar(stat="identity")+coord_flip()+xlab("City")+ylab("Mean Height (ft)")
```


# 3. Plot how many buildings are in each country
```{r}
Country=separate(data = tallb,col=City, into =c("City","Country"), sep ="\\(")
CCountry=separate(data = Country,col=Country, into =c("Country",NA), sep ="\\)")
CCountry
```

```{r}
library(countrycode)
CCountry$CountryName=countrycode(CCountry$Country,"iso2c", "country.name")
CCountry=CCountry[,-5]
```



```{r}
countrycounts=CCountry%>%group_by(CountryName)%>%summarize(number=length(CountryName))
ggplot(countrycounts,aes(reorder(CountryName,number),number))+geom_bar(stat="identity")+coord_flip()+xlab("Country Name")
```

# 4. Plot different cities based on mean height of buildings 
```{r}
meanc=CCountry%>%group_by(CountryName)%>%summarize(Mean =mean(`Height (ft)`))
meanc
```



```{r}
ggplot(meanc,aes(reorder(CountryName,Mean),Mean))+coord_flip()+geom_bar(stat="identity")+xlab("Country")

```

# 5. Color the bars in a graph that is based on the number of buildings in each country. 

```{r}
ggplot(countrycounts,aes(reorder(CountryName,number),number,fill=as.factor(CountryName)))+geom_bar(stat="identity",position="dodge")+coord_flip()+xlab("CountryName")

```

# 6. Building purpose and corresponding mean height
```{r}
tallb
uses=tallb%>%group_by(Use)%>%summarize(Mean=mean(`Height (ft)`))
uses
```


```{r}
ggplot(uses,aes(reorder(Use,Mean),Mean))+geom_bar(stat="identity",position = "dodge")+coord_flip()+ylab("Mean Height (ft)")+xlab("Use")
```


 